Rule Synthesis for Rule-based Intrusion Detectors

### 2020-06-01 paper/paper.tex
comment on V.E

%\subsubsection{Lack of comparison with other tools}
\noindent\textbf{Lack of comparison with other tools}
Table~\ref{table:comparison} summarizes the characteristics of
alternative techniques and provides details about the evaluation used
in corresponding papers. Unfortunately, side comparison was not
possible for three key reasons. First, we did not have access to the
tools. We tried, unsuccssefully, making contact with authors to obtain
the tools. Second, the tools output different objects. For that
reason, a comparison based on published results did not make sense. It
is important to recall that we did not report precision and recall as
it is 100\% always. \tname captures, by construction, all positive
traffic and does not capture any negative traffic. We used a stronger
criteria instead---the position of the correct rule in the ranking. It
is possible that other rules, higher in the ranking, are useful, but
only domain experts can identify that. Third, we are the only
technique to support content options, which are prevalent and
challenging to handle. A side comparison would be unfair if we
consider rules with those options.
\noindent\textbf{Running times.}~We ran all our tests using an
Intel(R) Xeon(R) CPU E3-1240 v6 and 8GB RAM. For attacks with only
categorical and numerical options, the average running time was 6
seconds per attack. For attacks with the content option, the average
running time was 1,445 seconds (=24.1 minutes).  \textbf{Threats to
  Validity.}~Considering external validity. Our results cannot be
generalized beyond the subjects we selected. To mitigate that threat
we selected a variety of attacks with different
characteristics. Unfortunately, we could not access tools for related
techniques, but there is strong evidence that \tname\ performs very
well and is the only technique to support content options, which are
very important in this domain. Considering internal validity, in
principle, the implementation of \tname\ could contain errors. We
mitigated that threat by carefully inspecting code and
results. Considering construct validity, the choice of ranking to
evaluate the approach may not be useful in practice. We considered the
use of ranking of the golden rule a reasonable choice as the approach
places the golden rule close to the top in most cases.

>>>>

%\subsubsection{Lack of comparison with other tools}
\noindent\textbf{Lack of comparison with other tools}
Table~\ref{table:comparison} summarizes the characteristics of
alternative techniques and provides details about the evaluation used
in corresponding papers. Unfortunately, side comparison was not
possible for three key reasons. First, we did not have access to the
tools. We tried, unsuccssefully, making contact with authors to obtain
the tools. Second, the tools output different objects. For that
reason, a comparison based on published results did not make sense. It
is important to recall that we did not report precision and recall as
it is 100\% always. \tname captures, by construction, all positive
traffic and does not capture any negative traffic. We used a stronger
criteria instead---the position of the correct rule in the ranking. It
is possible that other rules, higher in the ranking, are useful, but
only domain experts can identify that. Third, we are the only
technique to support content options, which are prevalent and
challenging to handle. A side comparison would be unfair if we
consider rules with those options.\Gui{I think that it's not good to say we are the only techinique to support content options. The other papers do not explain well how they support it, if they support for http (which is the most relevant one) or even if they support it at all. \cite{Kao2015AutomaticNR} manages contents in a similar way to ours, but it requires a manual step and their provided email doesn't even exist anymore. \cite{vollmer-etal-cics2011} and \cite{guruprasad} do not support http and don't explain well how they deal with ICMP contents. \cite{fallahi} technique deals with flows and not individual packets, so it doesn't even mention supporting contents.}
\noindent\textbf{Running times.}~We ran all our tests using an
Intel(R) Xeon(R) CPU E3-1240 v6 and 8GB RAM. For attacks with only
categorical and numerical options, the average running time was 6
seconds per attack. For attacks with the content option, the average
running time was 1,445 seconds (=24.1 minutes).  \textbf{Threats to
  Validity.}~Considering external validity. Our results cannot be
generalized beyond the subjects we selected. To mitigate that threat
we selected a variety of attacks with different
characteristics. Unfortunately, we could not access tools for related
techniques, but there is strong evidence that \tname\ performs very
well and is the only technique to support content options, which are
very important in this domain. Considering internal validity, in
principle, the implementation of \tname\ could contain errors. We
mitigated that threat by carefully inspecting code and
results. Considering construct validity, the choice of ranking to
evaluate the approach may not be useful in practice. We considered the
use of ranking of the golden rule a reasonable choice as the approach
places the golden rule close to the top in most cases.
